What do incoming university students believe about open science practices in

### 2021-04-01 analysis/Manuscript.Rmd
tidy version of correlations

The last decade has seen unprecedented change in methodological and reporting practices in psychology. These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that close replications of published psychological studies are often unable to replicate the original findings[@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018]. These apparent problems with replication have lead to a variety of potential solutions to make research practices more transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@simmons21WordSolution2012], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018]. These calls for more transparent research practices prompted the discipline to reflect on the norms and beliefs that underpin its practice of research. Many studies have polled researchers' understandings of and adherence to open science norms, beliefs, and practices [e.g., @baker500ScientistsLift2016; @openscienceworkinggroup2017SurveyOpen2018, @harrisUseReproducibleResearch2018). In turn, initiatives have been directed toward training undergraduate students in the adoption of an open science ethos [e.g., @chopikHowWhetherTeach2018; @graheHarnessingUndiscoveredResource2012, @jekelHowTeachOpen2020, @schonbrodtTrainingStudentsOpen2019].  These initiatives help engrain open science norms and change attitudes about research practices, but we know little about what these students know or believe about open science research practices prior to entering the university classroom.

The most comprehensive set of principles for how science *ought* to be practiced are Merton's (1942) norms of science. Scientists (Anderson et al., 2000) and graduate students (Anderson & Louis, 1994) alike have historically endorsed the normative value of Merton's principles. Furthermore, many of the recent practices designed to make science more transparent and open reflect Mertonian norms. For example, the practice of sharing open source software directly corresponds to the Mertonian norm of *communism*: Scientists should have common ownership of scientific goods. Similarly, the practices of sharing of preprints for open peer review and open data for checking of reproducibility corresponds to the norm of communality, but also to that of *organised skepticism*: Scientific claims should be subjected to critical scrutiny. Preregistration can be connected to the norm of *disinterestedness*: By making (and preregistering) decisions about how to analyse data before results are produced, a researcher can limit the degree to which the substantive results produced by different analytic strategies affect their decisions regarding which analyses to report. In this sense, the ongoing reform in psychological research can partly be understood as simultaneously a set of new practices and a re-affirmation of old norms.

Nevertheless, rapid changes in methodological practice and empirical findings present significant pedagogical challenges for the teacher of psychology. Keeping textbooks and other instructional materials up to date is  difficult when supposedly well-established findings are being contradicted by new replications emerging at a rapid pace. Furthermore, training in emerging methodological practices is crucial for graduate students who may go on to apply psychological research methods themselves, so that thay may produce research that is even more replicable than that of previous generations. Even for students who do not go on to conduct research themselves, an understanding of contemporary methodological practices - and problems with methodological practices in psychology - is essential for becoming informed and critical consumers of psychological knowledge. However, how we best provide this understanding is no trivial task. Indeed, there are several reasons why it might be unwise to assume a simple knowledge deficit, where the teacher's only role is to dispense an understanding of open science and transparent research practices.

@@

Second, when psychology students are beginning their university studies, they are often learning for the first time about how and why it is useful to apply scientific methods to studying human behaviour (rather than only relying on alternative sources of knowledge such as intuition or anecdote or authority). Could an over-emphasis on problems with replicability leave such students unconvinced that scientific methods for studying human behaviour are valuable *at all*, leaving them to favour even less credible alternative sources of knowledge? It is therefore important to determine what levels of trust in psychological research (and its replicability) are prevalent in incoming undergraduate students. In their examination of the usefulness of a one-hour lecture about the replication crisis, @chopikHowWhetherTeach2018 found that undergraduate students trusted the results of studies by psychologists less after the lecture than they did before it, although the effect size was fairly small (d = -.36), and mean trust levels remained fairly high after the lecture (M = 4.94 on a scale of 1 to 7).

Third, anecdotal evidence suggests that students being taught about open science practices and reforms to improve reproducibility (such as open sharing of data and analysis code) are often surprised that this is not *already* standard practice. In other words, students' naive conception of how science works may in some ways be closer to that embodied in recent reforms rather than "business as usual" practices. Indeed, surveys of scientists' subscriptions to Mertonian norms have often found that while most scientists endorse Mertonian norms such as communality, universalism and disinterestedness, this is by no means the case for all scientists. Furthermore, they typically perceive the behaviour of other scientists as being less consistent with these norms than their own [@andersonNormativeDissonanceScience2007]. It is thus possible that, for some students, teaching about reform may be less a matter of conveying new information and more one of reinforcing "naive" assumptions. In fact, although beyond the scope of this article, it is *possible* that incoming undergraduate students more strongly endorse open science norms than do academics.

@@

<!-- I'm not sure about the argument in the above paragraph - might be somewhat of a stretch? -->

@@

Our approach to measuring norms and counternorms focussed on participants' evaluation of ten specific open science practices that reflected diverse open science norms rather than trying to measure endorsement of the more abstract Mertonian norms (cf. Anderson et al., 2007). <!-- Mention here our discussions workshopping of common open science norms at SIPs? ! -->
The open science practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficent information of replicability, preprints, open materials, open data, and open access publishing. Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." There were 20 scenarios in total.
For example, the practice of posting article preprints was evaluated with the pro-open science item: "Deborah should post a manuscript describing the Findings of her study openly online as soon as it is complete, even if the manuscript has not yet been checked by experts (peer reviewed) and accepted for publication in a journal." The counter-open preprint item read: "Deborah should not post a manuscript describing the findings of her study online until after it has been checked by experts (peer reviewed) and accepted for publication in a journal." Participants rated their agreement with each prescriptive statement on a 1 (strongly disagree) to 5 (strongly agree) scale.

### Norms in Practice

We also sought to measure participants' normative beliefs about how psychological science was actually conducted by researchers around the world. To that end we asked participants, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" The ten characteristics explicitly described each of the ten open science practices named above. For example, "A manuscript describing the findings of the study is posted openly online as soon as it is complete, even if the manuscript has not yet been checked by experts (peer reviewed) and accepted for publication in a journal." Participants were given a slider bar ranging from 0% to 100% to record their estimate.

@@

In line with our preregisterd analysis plan, we cacluated the difference in means
between responses to each norm item and its accompanying counternorm, along with 
95% confidence intervals. For this analysis, we removed three cases with missing values. 
Table XX displays the means and standard deviations for each norm, counternorm, 
and the difference values.

@@

 # \@ref(tab:chunk-name)  [JB removed this from the text above to see if that solves
  # our table caption issue]

# select columns that relate to norms & pivot it long
norm_long <- df %>% 
  select(c(id, ends_with("_norm"))) %>% 
    pivot_longer (cols = ends_with("norm"),
                names_to = "practice",
                values_to = "norm rating")

@@

# select columns that relate to counternorms
cnorm_long <- df %>% 
  select(c(id, ends_with("_cnorm"))) %>% 
  pivot_longer (cols = ends_with("cnorm"),
                names_to = "practice",
                values_to = "cnorm rating")

@@

# create a `diff` variable that is the counternorm subtracted from the norm
norm_cnorm <- norm_cnorm %>% 
  mutate (diff = (`norm rating` - `cnorm rating`)) %>% 
    drop_na() %>% # drop the three NA values
      dplyr::select(-(`id`)) # remove this now that I've confirmed it works

# get the n values for each of the practices
prac_counts <- norm_cnorm %>% 
    dplyr::group_by(practice) %>%  
    count()

# calculate means
prac_ms_sds <- norm_cnorm %>% 
    dplyr::group_by(practice) %>%  
    summarise(norm_mean = mean(`norm rating`), 
              norm_sd = sd(`norm rating`),
              cnorm_mean = mean(`cnorm rating`), 
              cnorm_sd = sd(`cnorm rating`),
              diff_mean = mean(`diff`), 
              diff_sd = sd(`diff`)) %>% 
  ungroup()

@@

# combine means & SDs
prac_means$Norm <- paste0(round_tidy(prac_means$norm_mean,2),
                          " (", 
                          round_tidy(prac_means$norm_sd,2), 
                          ")")
prac_means$Counternorm <- paste0(round_tidy(prac_means$cnorm_mean,2), 
                            " (", 
                            round_tidy(prac_means$cnorm_sd,2), 
                            ")")
prac_means$Difference <- paste0(round_tidy(prac_means$diff_mean,2), 
                            " (", 
                            round_tidy(prac_means$diff_sd,2),
                            ")", 
                            " [",
                            round_tidy(prac_means$lower,2),
                            ", ", 
                            round_tidy(prac_means$upper,2),
                            "]")

# clean it up into a new dataframe with only the columns we need
practice_means <- prac_means %>% 
  select(practice,Norm, Counternorm, Difference)

@@

critical_corr <- round(cor(df$critical_norm, df$critical_cnorm),2)

@@

# breadcrumbs: when I come back to this, I need to combine these in a tibble
  # and then join it with the existing table...
critical_corr <- round(cor(df$critical_norm, df$critical_cnorm),2)
critical_CI <- round(CIr(r = critical_corr, n = nrow(df), level = 0.95),2)

>>>>

The last decade has seen unprecedented change in methodological and reporting practices in psychology. These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that close replications of published psychological studies are often unable to replicate the original findings[@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018]. These apparent problems with replication have lead to a variety of potential solutions to make research practices more transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@simmons21WordSolution2012], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018]. These calls for more transparent research practices prompted the discipline to reflect on the norms and beliefs that underpin its practice of research. Many studies have polled researchers' understandings of and adherence to open science norms, beliefs, and practices [e.g., @baker500ScientistsLift2016; @openscienceworkinggroup2017SurveyOpen2018, @harrisUseReproducibleResearch2018). In turn, initiatives have been directed toward training undergraduate students in the adoption of an open science ethos [e.g., @chopikHowWhetherTeach2018; @graheHarnessingUndiscoveredResource2012, @jekelHowTeachOpen2020, @schonbrodtTrainingStudentsOpen2019].  These initiatives help ingrain open science norms and change attitudes about research practices, but we know little about what these students know or believe about open science research practices prior to entering the university classroom.

The most comprehensive set of principles for how science *ought* to be practiced are Merton's (1942) norms of science. Scientists (Anderson et al., 2000) and graduate students (Anderson & Louis, 1994) alike have historically endorsed the normative value of Merton's principles. Furthermore, many of the recent practices designed to make science more transparent and open reflect Mertonian norms. For example, the practice of sharing open source software directly corresponds to the Mertonian norm of *communism*: Scientists should have common ownership of scientific goods. Similarly, the practices of sharing of preprints for open peer review and open data for checking of reproducibility corresponds to the norm of communality, but also to that of *organised skepticism*: Scientific claims should be subjected to critical scrutiny. Preregistration can be connected to the norm of *disinterestedness*: By making (and preregistering) decisions about how to analyse data before results are produced, a researcher can limit the degree to which the substantive results produced by different analytic strategies affect their decisions regarding which analyses to report. In this sense, the ongoing reform in psychological research can partly be understood as simultaneously a set of new practices and a re-affirmation of established norms.

Nevertheless, rapid changes in methodological practice and empirical findings present significant pedagogical challenges for the teacher of psychology. Keeping textbooks and other instructional materials up to date is difficult when supposedly well-established findings are contradicted by new replications emerging at a rapid pace. Furthermore, training in emerging methodological practices is crucial for graduate students who may go on to apply psychological research methods themselves, so that they may produce research that is even more replicable than that of previous generations. Even for students who do not go on to conduct research themselves, an understanding of contemporary methodological practices - and problems with methodological practices in psychology - is essential for becoming informed and critical consumers of psychological knowledge. However, how we best provide this understanding is no trivial task. Indeed, there are several reasons why it might be unwise to assume a simple knowledge deficit, where the teacher's only role is to dispense an understanding of open science and transparent research practices.

@@

Second, when psychology students are beginning their university studies, they are often learning for the first time about how and why it is useful to apply scientific methods to studying human behaviour (rather than only relying on alternative sources of knowledge such as intuition or anecdote or authority). An over-emphasis on problems with replicability could leave these students unconvinced that scientific methods for studying human behaviour are valuable *at all*, leaving them to favour even less credible alternative sources of knowledge? For instance, @chopikHowWhetherTeach2018 found that undergraduate students tended to trust the results of psychological studies *less* after a one-hour educational lecture about the replication crisis[^1]. 
[^1]: Notably, the effect of the lecture on trust of psychological stuides was relatively small (d = -.36), and mean trust levels remained fairly high after the lecture (M = 4.94 on a scale of 1 to 7).

Third, anecdotal evidence suggests that students being taught about open science practices and reforms to improve reproducibility (such as open sharing of data and analysis code) are often surprised that this is not *already* standard practice. In other words, students' naive conception of how science works may, in some ways, be closer to that embodied in recent reforms rather than "business as usual" practices. Indeed, surveys of scientists' subscriptions to Mertonian norms have often found that while most scientists endorse Mertonian norms such as communality, universalism and disinterestedness, this is by no means the case for all scientists. Furthermore, they typically perceive the behaviour of other scientists as being less consistent with these norms than their own [@andersonNormativeDissonanceScience2007]. Therefore - for some students - teaching about reform may be less a matter of conveying new information and more one of reinforcing "naive" assumptions. In fact, although beyond the scope of this article, it is *possible* that incoming undergraduate students more strongly endorse open science norms than do academics.

@@

<!-- I'm not sure about the argument in the above paragraph - might be somewhat of a stretch? 
MP: Maybe a stretch, but given we have a good rationale already, it might be worth trying to keep it. We may need a reference to two to help make some of the claims more concrete though.-->

@@

### Open Science Norms and Counternorms

Our approach to measuring norms and counternorms focussed on participants' evaluation of ten specific open science practices that reflected diverse open science norms rather than trying to measure endorsement of the more abstract Mertonian norms (cf. Anderson et al., 2007). <!-- Mention here our discussions workshopping of common open science norms at SIPs? ! -->
The open science practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficent information of replicability, preprints, open materials, open data, and open access publishing. Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." There were 20 scenarios in total (see Table X). Participants rated their agreement with each prescriptive statement on a 1 (strongly disagree) to 5 (strongly agree) scale.

<!-- Add Table X of norms and counternorms statements that map to each practice -->

### Beliefs About the Practice of Psychological Science

We also sought to measure participants' normative beliefs about how psychological science was actually conducted by researchers around the world. To that end we asked participants, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" The ten characteristics explicitly described each of the ten open science practices (see Table XX). Participants were given a slider bar ranging from 0% to 100% to record their estimate.

<!-- Add Table XX of 10 belief statements -->

@@

In line with our preregisterd analysis plan, we calculated the difference in means
between responses to each norm item and its accompanying counternorm, along with 
95% confidence intervals. For this analysis, we removed three cases with missing values. 
Table XX displays the means and standard deviations for each norm, counternorm, 
and the difference values.

\@ref(tab:chunk-name)

@@

# select columns that relate to norms & pivot it long
norm_long <- df %>% 
  dplyr::select(c(id, ends_with("_norm"))) %>% 
    pivot_longer (cols = ends_with("norm"),
                names_to = "practice",
                values_to = "norm rating")

@@

# select columns that relate to counternorms
cnorm_long <- df %>% 
  dplyr::select(c(id, ends_with("_cnorm"))) %>% 
  pivot_longer (cols = ends_with("cnorm"),
                names_to = "practice",
                values_to = "cnorm rating")

@@

# create a `diff` variable that is the counternorm subtracted from the norm
norm_cnorm_long <- norm_cnorm %>% 
  mutate (diff = (`norm rating` - `cnorm rating`)) %>% 
    drop_na() %>% # drop the three NA values
      dplyr::select(-(`id`)) # remove this now that I've confirmed it works

# get the n values for each of the practices
prac_counts <- norm_cnorm_long %>% 
    dplyr::group_by(practice) %>%  
    count() %>% 
  ungroup()

# calculate means
prac_ms_sds <- norm_cnorm_long %>% 
    dplyr::group_by(practice) %>%  
    summarise(norm_mean = mean(`norm rating`), 
              norm_sd = sd(`norm rating`),
              cnorm_mean = mean(`cnorm rating`), 
              cnorm_sd = sd(`cnorm rating`),
              diff_mean = mean(`diff`), 
              diff_sd = sd(`diff`)) %>% 
  ungroup()

@@

# combine means & SDs
prac_means$Practice <- prac_means$practice
prac_means$Norm <- paste0(round_tidy(prac_means$norm_mean,2),
                          " (", 
                          round_tidy(prac_means$norm_sd,2), 
                          ")")
prac_means$Counternorm <- paste0(round_tidy(prac_means$cnorm_mean,2), 
                            " (", 
                            round_tidy(prac_means$cnorm_sd,2), 
                            ")")
prac_means$Difference <- paste0(round_tidy(prac_means$diff_mean,2), 
                            " (", 
                            round_tidy(prac_means$diff_sd,2),
                            ")", 
                            " [",
                            round_tidy(prac_means$lower,2),
                            ", ", 
                            round_tidy(prac_means$upper,2),
                            "]")

# clean it up into a new dataframe with only the columns we need
practice_means <- prac_means %>% 
  dplyr::select(Practice, Norm, Counternorm, Difference)

@@

# notes for the correlations....
# just the correlation with CI
critical_corr <- round(cor(df$critical_norm, df$critical_cnorm),2)
critical_CI <- round(CIr(r = critical_corr, n = nrow(df), level = 0.95),2)

#correlation test with CI and p-values in a clean tibble
critical_corr_test <- cor.test(df$critical_norm, df$critical_cnorm)
tidy(critical_corr_test)

cor(df$`norm rating`, df$`cnorm rating`)

# use this tutorial to try to get the correlations for each practice (using the long data)
# https://cran.r-project.org/web/packages/broom/vignettes/broom_and_dplyr.html

# this will create a tibble for each practice and then calculate

# calculates the correlation test for each tibble & then tidies it up
corr <- norm_cnorm_long %>% 
  nest(data = -practice) %>% # create a tibble for each practice
  mutate (test = map(data, ~ cor.test(.x$`norm rating`, .x$`cnorm rating`)), 
          tidied = map(test,tidy)) %>% # run the corr & tidy it
  unnest(tidied) # unnest it to look at the results

# breadcrumbs: keep the values that I need from this tibble
# use p_tidy? to clean up the pvalues
# round the corr & CI
# join with the practice_means tibble & turn into a table

@@

# breadcrumbs: when I come back to this, I need to combine these in a tibble
  # and then join it with the existing table...I probably need to mutate, but I 
  # need to sort out how to do this...

# practice_corr <- practice_means %>% 
  # mutate()

critical_corr <- round(cor(df$critical_norm, df$critical_cnorm),2)
critical_CI <- round(CIr(r = critical_corr, n = nrow(df), level = 0.95),2)
